---
title: "Signature Analysis: SigScores"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3
---

# Background

-   This script is dedicated to the generation of the visualisations for `SigScores` results for the HCC1806 data. The visualisations we are going are the following:

    -   **Heatmaps:** rows as cells, signatures as columns, and values as a single signature scoring metric. For N signature scoring metrics, we will have N heatmaps.

    -   **3D UMAP Plots:** The generic UMAP plots do not look nice on this data because of its size and the scatter of the points, which is not aesthetically pleasing in the least. For this reason, we are going with a 3D plot where the z-axis is the signature score.

    -   **Density Plots:** These show the density of the signature score for the hypoxic and normoxic populations in our signature of interest vs the simulations.

# Packages

```{r}
shhh <- suppressPackageStartupMessages
#Tidyverse
shhh(library(tidyverse))
shhh(library(viridis)) 
shhh(library(patchwork)) 
shhh(library(RColorBrewer)) 
shhh(library(scales))
shhh(library(tictoc))
shhh(library(fs))
shhh(library(ShinyCell))
shhh(library(plotly))
shhh(library(ggthemes))
shhh(library(ggdist))


#Bioconductor
shhh(library(Matrix))
shhh(library(glmGamPoi)) 
shhh(library(clustree)) 
shhh(library(org.Hs.eg.db)) 
shhh(library(biomaRt))

#Seurat
shhh(library(Seurat))
shhh(library(SeuratDisk))
shhh(library(SeuratWrappers))

#waddR
# BiocManager::install("waddR")
shhh(library(waddR))

#Setting Working Directory
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

# Seurat Data Import

```{r}
# HCC1806 Seurat
HCC1806NISub <- LoadH5Seurat(file = "../SigScores.Cluster/HCC1806/Read/HCC1806NISub.h5seurat")

# PCA & UMAP
HCC1806NISub <- HCC1806NISub %>% RunPCA()
HCC1806NISub <- HCC1806NISub %>% RunUMAP(reduction = "pca", dims = 1:20)

# Cell Cycle Scoring
HCC1806NISub <- CellCycleScoring(HCC1806NISub, 
                                 #S phase features
                                 s.features = cc.genes.updated.2019$s.genes,
                                 #G2/M phase features
                                 g2m.features = cc.genes.updated.2019$g2m.gene,
                                 #set assay identity
                                 set.ident = TRUE)
```

# SigScores Results Import

-   The import is a little complicated because every single signature has its own file, so the code below aims to achieve the following:

    -   Load all of the signature scoring results into an R list with different elements being the different signatures.

    -   Use intelligent string manipulation to attach signature names to the different R list slots.

    -   Remove a useless column in the results (`…1`) that is probably some artifact of saving.

```{r}
# Signatures Import & List Naming
filepaths <- fs::dir_ls(path = "../SigScores.Cluster/HCC1806/Write/Tables/SigScores/Composite/")
signatures <- map(filepaths, function(path){
  readr::read_csv(file = path, col_names = T)})
names(signatures) <- str_split(str_split(string = names(signatures),
                                                   pattern = "/",
                                                   simplify = T)[,8],
                               pattern = "\\.",
                               simplify = T)[,1]
# List Cleanup
signatures <- map(.x = signatures,.f = function(x){
  x <- x %>% dplyr::select(-...1)
  return(x)
})

# Available Scores
my_scores <- signatures$Aprelikova_2006 %>% dplyr::select(-c(sampleID, run, Condition)) %>% colnames()
```

# SigScores Results Visualisation

## UMAP Plots

-   In the very first instance, visualization are going to be UMAP plots with the colors of the points being the different signature scores.

    -   Signature scores are going to be for the different scoring metrics available in sigscores, which are available in `sigscores::getAvailableScores()`.

        -   Implicit in my focus here is the neglection of the random simulations I ran because they add literally nothing to the visualisation front for single cell data, where UMAP plots are significantly more attractive.

    -   The aim is to save the signature data to the Seurat object in a way that allows for sigantures scores to be visualized using a Shiny App. This would then automate the exploration of results as well as the generation of relevant figures that are suitable for the publication.

-   Other forms of visualisation are possible, such as a histogram of WD distances for signature of interest vs random simulations for the different scores. The issue with these figures is that they are tedious, repetitive, and aesthetically repulsive, hence why I am focusing a lot on the UMAP plots, which look significantly nicer.

-   Below is my solution for visualisation, and that is the addition of the signature scores of each signature to the metadata of my Seurat object, use the new Seurat object to create shiny app (**ShinyCell**), and use the apps as the primary form of visualisation.

```{r}
map(names(signatures), function(sig_name){
  sig_app_dir <- paste0("../Write/Apps/HCC1806/Signatures/",sig_name,"/") 
  dir.create(sig_app_dir,
             recursive = T)
  HCC1806NISub <- Seurat::AddMetaData(object = HCC1806NISub,
                                      metadata = signatures[[sig_name]] %>%
                                        dplyr::filter(run == 0) %>%
                                        column_to_rownames("sampleID"))
  scConf <- createConfig(HCC1806NISub)
  makeShinyApp(obj = HCC1806NISub,
               scConf = scConf, 
               gene.mapping = TRUE,
               gex.assay = "SCT",
               gex.slot = "data",
               shiny.title = paste0("HCC1806: ", sig_name),
               shiny.dir = sig_app_dir)
})
```

## 3D UMAP Plots

-   These are exactly the same UMAP plots I generated but with the addition of a z-axis showing the specific signature score.

-   I have not done 3D UMAP plots before but I know they are easy to generate using [**plotly in R**](https://plotly.com/r/3d-scatter-plots/), and this is what I intend to use. The only issue I have with this is the saving, but I think I will have to figure that out midway.

    -   The saving is done using the `orca()` function, which you have to download using special instructions first. That has already been done and the saving is now configured.

        -   The only things left to figure out are customisation of point size in the figure (current point size is very large for no reason) and configuration of angle of view for saving (default angle is rather bad and does not show the separation well along the different axes).

-   The essential steps are the following:

    -   Pull out the UMAP data.

    -   Add that to the Seurat object metadata.

    -   Use the metadata dataframe to plot the 3D UMAP plot.

### Singular Implementation

-   For the singular implementation below, the original goal was to develop the code that would then be scaled to every combination of score and signature. This goal has been achieved.

-   The second goal now is to customize the figure that we are going to be using in the publication by modifying point size and angle of view manually (not going to be done for other figures).

-   The representative signature and score are **Tardon_2020** and **IQM**.

```{r}
# metadata annotation
HCC1806NISub_Tardon <- Seurat::AddMetaData(object = HCC1806NISub,
                                               metadata = signatures$Tardon_2020 %>%
                                                 dplyr::filter(run == 0) %>%
                                                 column_to_rownames("sampleID"))
HCC1806NISub_Tardon <- Seurat::AddMetaData(object = HCC1806NISub_Tardon,
                                               metadata = data.frame(HCC1806NISub_Tardon@reductions$umap@cell.embeddings))

# 3D UMAP Plot
p1 <- plot_ly(
  x = HCC1806NISub_Tardon@meta.data$UMAP_1, 
  y = HCC1806NISub_Tardon@meta.data$UMAP_2, 
  z = HCC1806NISub_Tardon@meta.data$iqm, 
  color = HCC1806NISub_Tardon@meta.data$Condition, 
  colors = c('#0C4B8E', '#BF382A'),
  size = I(100)) %>%
  add_markers() %>%
  layout(title = "Tardon IQM",
         scene = list(
                      xaxis = list(title = 'UMAP1'),
                      yaxis = list(title = 'UMAP2'),
                      zaxis = list(title = 'IQM', 
                                   range = c(0, 1000), 
                                   type = "linear"),
                      camera = list(eye = list(x = -3, y = 3, z = 2))))
p1
# orca(p1, 
#      file = "Tardon_IQM",
#      scale = 10, 
#      height = 1000,
#      width = 1000)
```

### Scaled Up Implementation

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main), 
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_umap <- map(signatures_main_annotated, function(sig_df){
  sig_df <- sig_df %>% left_join(data.frame(HCC1806NISub@reductions$umap@cell.embeddings) %>% 
                         rownames_to_column("sampleID"))
  return(sig_df)
})
# available scores
available_scores <- my_scores

# Double Map Call for 3D Umap Creation
tic()
umap_plots <- map(names(signatures_main_annotated_umap),
                     .f = function(sig_df_name){
  map(available_scores, function(score_name){
    current_sig <- signatures_main_annotated_umap[[sig_df_name]]
    p1 <- plot_ly(
      x = current_sig[["UMAP_1"]],
      y = current_sig[["UMAP_2"]], 
      z = current_sig[[score_name]], 
      color = current_sig[["Condition"]], 
      colors = c('#0C4B8E', '#BF382A'),
      size = I(100)) %>%
      add_markers() %>%
      layout(title = paste0(sig_df_name, " ", score_name),
             scene = list(
               xaxis = list(title = 'UMAP1'),
               yaxis = list(title = 'UMAP2'),
               zaxis = list(title = score_name, 
                            range = c(0,1000),
                            type = "linear"),
               camera = list(eye = list(x = -2, y = 2, z = 2))))
    return(p1)
  }) %>% setNames(available_scores)
  }) %>% setNames(names(signatures_main_annotated_umap))

# Map Call for Directory Creation Per Signature
map(names(signatures_main_annotated_umap), function(sig_name){
  dir.create(path = paste0("../Write/Figures/3D/HCC1806/",sig_name),
             recursive = TRUE)})

# Double Map Call for Saving Each Score Figure Per Signature
map(names(umap_plots), function(sig_name){
  map(available_scores, function(score_name){
    orca(p = umap_plots[[sig_name]][[score_name]],
         file = paste0("../Write/Figures/3D/HCC1806/",
                       sig_name, "/",
                       score_name,".jpeg"),
         scale = 10, 
         height = 1000,
         width = 1000)
  })
})
toc()
```

## Heatmaps

### Base Heatmaps

#### Manual Color Scale

-   The structure of the heatmaps below is such that the rows are the cells, the columns are the signatures, and the values are that for a particular score. Given N scores, we generate N heatmaps per cell line.

-   For the heatmap below, I did a few wrangling steps that achieved the following:

    -   Filter for run 0 (simulations are being ignored at this point).

    -   Annotate the signatures dataframes with the signature names.

    -   `rbind()` all the signature dfs within the signatures list.

    -   `pivot_wider()` for a single score such that the columns are the values for the different signatures, and the rows are the cells (which will be annotated by their condition).

-   Automation was done at the single score level such that the `pivot_wider()` starts from the score of interest. I have also modified the color range for each heatmap such that there are at least 4 break marks (**min**, **1st quantile**, **median**, **3rd quantile**).

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Score Heatmaps
scores <- sigscores::getAvailableScores() %>% dplyr::filter(!id %in% c("mode","iqm")) %>% pull(id)
score_heatmaps <- map(scores, function(score_name){

  ## Wrangling
  signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = all_of(score_name),
              id_cols = c(sampleID,Condition)) %>%
  arrange(Condition)


  ## Matrix Generation
  mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()

  ## color function
  starting_point <- summary(signatures_main_annotated_rbind %>%
                              dplyr::pull(all_of(score_name)))[1]
  first_quantile <- summary(signatures_main_annotated_rbind %>%
                              dplyr::pull(all_of(score_name)))[2]
  median_value <- summary(signatures_main_annotated_rbind %>%
                            dplyr::pull(all_of(score_name)))[3]
  third_quantile <- summary(signatures_main_annotated_rbind %>%
                              dplyr::pull(all_of(score_name)))[5]

  col_fun <- circlize::colorRamp2(breaks = c(starting_point,
                                             first_quantile,
                                             median_value,
                                             third_quantile),
                                  colors = c("blue",
                                                   "green",
                                                   "yellow",
                                                   "red"))


  ## row annotation
  row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = "blue",
                                                          "Normoxia" = "red"))
                                          )


  h1 <- ComplexHeatmap::Heatmap(matrix = mat,
                          show_row_names = F,
                          name = score_name,
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha,
                          # Color Function (To Control for Outliers)
                          col = col_fun)
  return(h1)
})
names(score_heatmaps) <- scores
# Saving
dir.create("../Write/Figures/Heatmaps/HCC1806/")
map(names(score_heatmaps), function(score_name){
      png(file = paste0("../Write/Figures/Heatmaps/HCC1806/", score_name,".png"),
          width = 1000,
          height = 1000)
  print(score_heatmaps[[score_name]])
  dev.off()
      })
```

#### Automatic Color Scale

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Score Heatmaps
scores <- sigscores::getAvailableScores() %>% dplyr::filter(!id %in% c("mode","iqm")) %>% pull(id)
score_heatmaps <- map(scores, function(score_name){

  ## Wrangling
  signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = all_of(score_name),
              id_cols = c(sampleID,Condition)) %>%
  arrange(Condition)


  ## Matrix Generation
  mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()


  ## row annotation
  row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = "blue",
                                                          "Normoxia" = "red"))
                                          )


  h1 <- ComplexHeatmap::Heatmap(matrix = mat,
                          show_row_names = F,
                          name = score_name,
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha
                          # Color Function (To Control for Outliers)
                          # col = col_fun
                          )
  return(h1)
})
names(score_heatmaps) <- scores
# Saving
dir.create("../Write/Figures/Heatmaps_NEW/HCC1806/",recursive = T)
map(names(score_heatmaps), function(score_name){
      png(file = paste0("../Write/Figures/Heatmaps_NEW/HCC1806/", score_name,".png"),
          width = 1000,
          height = 1000)
  print(score_heatmaps[[score_name]])
  dev.off()
      })
```

### Z-Scoring Heatmaps

#### Singular Implementation

```{r}
## Wrangling
signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = iqm,
              id_cols = c(sampleID,Condition)) %>%
  arrange(Condition)

## Matrix Generation
mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()
scaled_mat <- scale(mat)


## row annotation
row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = "blue",
                                                          "Normoxia" = "red"))
                                          )


h1 <- ComplexHeatmap::Heatmap(matrix = scaled_mat,
                          show_row_names = F,
                          name = "iqm",
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off column clustering
                          cluster_columns = F,
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha,
                          # Color Function (To Control for Outliers)
                          # col = col_fun
                          )
```

#### Scaled Implementation

-   These heatmaps are identical to the ones above with one key difference: `z-scoring`. The reason z-scoring is applied is to account for the massive discrepancy in the scales for the different signatures within the same score.

    -   z-scoring will be done per columns/signatures for every single score, and the manual color scale that was based on quantiles below will be removed.

-   The second modification is the addition of the p-values for the WD distances between the hypoxic and normoxic samples for the different signatures within the same score as a column annotation within ComplexHeatmap.

    -   I could go for either the WD distances themselves as barplot annotations or with the p-values as a mini-heatmap (base annotation type).

-   The third modification is the removal of clustering per columns, and the ordering of the columns/signatures alphabetically to match Matteo's signatures.

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Score Heatmaps
scores <- sigscores::getAvailableScores() %>% 
#  dplyr::filter(!id %in% c("mode","iqm")) %>% 
  pull(id)

score_heatmaps <- map(scores, function(score_name){

  ## Wrangling
  signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = all_of(score_name),
              id_cols = c(sampleID,Condition)) %>%
  arrange(Condition)

  ## Matrix Generation
  mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()
  
  ## z-scoring
  scaled_mat <- scale(mat)
  ## color function
  # starting_point <- summary(signatures_main_annotated_rbind %>%
  #                             dplyr::pull(all_of(score_name)))[1]
  # first_quantile <- summary(signatures_main_annotated_rbind %>%
  #                             dplyr::pull(all_of(score_name)))[2]
  # median_value <- summary(signatures_main_annotated_rbind %>%
  #                           dplyr::pull(all_of(score_name)))[3]
  # third_quantile <- summary(signatures_main_annotated_rbind %>%
  #                             dplyr::pull(all_of(score_name)))[5]
  # 
  # col_fun <- circlize::colorRamp2(breaks = c(starting_point,
  #                                            first_quantile,
  #                                            median_value,
  #                                            third_quantile),
  #                                 colors = c("blue",
  #                                                  "green",
  #                                                  "yellow",
  #                                                  "red"))


  ## row annotation
  row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = "blue",
                                                          "Normoxia" = "red")
                                          ))


  h1 <- ComplexHeatmap::Heatmap(matrix = scaled_mat,
                          show_row_names = F,
                          name = score_name,
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off column clustering
                          cluster_columns = F,
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha,
                          # Color Function (To Control for Outliers)
                          # col = col_fun
                          )
  return(h1)
})
names(score_heatmaps) <- scores
# Saving
dir.create("../Write/Figures/Heatmaps_ZScore/HCC1806/", recursive = T)
map(names(score_heatmaps), function(score_name){
      png(file = paste0("../Write/Figures/Heatmaps_ZScore/HCC1806/", score_name,".png"),
          width = 1000,
          height = 1000)
  print(score_heatmaps[[score_name]])
  dev.off()
      })
```

#### Scaled Implementation + Column Annotations

-   This section is identical to the one before with the addition of column annotations for accuracy values, WD values, and p-values for the signatures.

    -   Accuracy values will come from Matteo's bulk analysis and will be super-imposed on the heatmap for the single cell data to facilitate comparison.

    -   WD values are going to come from the distributions of the hypoxic and normoxic scores in our signature of interest. Simulations are not relevant at this point

    -   p-values will accompany the WD values.

-   This section is divided into two sections:

    -   Section 1 is for the computation of the needed WD distance and p-values.

        -   For this section, this analysis has already been done before; the code has a different structure to the one I am using now (separate lists instead of a single dataframe and WD distance calculation for all runs including simulations), so I will adjust as needed.

    -   Section 2 is for adding that information to my heatmap.

-   `Note`: when running the WD analysis, an issue came up with He_2021 because of NA values in the IQM score, which is already an issue we are aware of from the heatmaps.

    -   I check the heatmaps of missing genes for each signature that I generated a while ago, but they don't seem to have my signature; that probably means they require an update because they are not using. all the signatures I am now including in this analysis. This is a `follow-up task`.

##### WD Calculation (Original Alone)

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Replacing NA Values
signatures_main <- map(.x = signatures_main, .f = function(sig_df){
  sig_df <- sig_df %>% replace_na(replace = list(iqm = 0)) %>% dplyr::mutate(iqm = as.numeric(iqm))
  return(sig_df)
})

# WD Distance Calculation
## WD Metrics
spec.output <- c("pval","d.wass^2","perc.loc","perc.size","perc.shape")

## Calculation Code
tic()
signatures_metrics_wd <- map(names(signatures_main),
                             function(sig_name){
                               map(sigscores::getAvailableScores()$id,
                                   function(score){
                                     
                                     # Hypoxic Scores
                                     v1 <- signatures_main[[sig_name]] %>%
                                     dplyr::filter(Condition == "Hypoxia") %>%
                                     pull(score)
                                     
                                     # Normoxic Scores
                                     v2 <- signatures_main[[sig_name]] %>%
                                     dplyr::filter(Condition == "Normoxia") %>%
                                     pull(score)
                                     
                                     # WD Function
                                     wd <- waddR::wasserstein.test(x = v1, y = v2, method = "ASY")[spec.output]
                                     return(wd)
      }) %>% setNames(sigscores::getAvailableScores()$id)
                             }) %>% setNames(names(signatures_main))
toc() # 40 seconds (quick because we are only focusing on the main run with no simulations added)
signatures_metrics_wd$Aprelikova_2006
# saveRDS(object = signatures_metrics_wd, file = "../Intermediate/HCC1806_Signatures_Metrics_WD.rds")

## rbind results (single df)
signatures_metrics_wd_rbind <- map(names(signatures_metrics_wd),
    function(sig_name){
        aggregated_score <- do.call(rbind, signatures_metrics_wd[[sig_name]]) %>% 
          data.frame() %>% 
          rownames_to_column("score") %>%
          dplyr::mutate(signature = rep(sig_name, nrow(.)))
        }) %>% setNames(names(signatures_metrics_wd))
signatures_metrics_wd_rbind_df <- do.call(rbind, signatures_metrics_wd_rbind)
rownames(signatures_metrics_wd_rbind_df) <- NULL
```

##### Heatmap Function (WD Calculation) (Original Alone)

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Score Heatmaps
scores <- sigscores::getAvailableScores() %>% 
#  dplyr::filter(!id %in% c("mode","iqm")) %>% 
  pull(id)

score_heatmaps <- map(scores[-7], function(score_name){

  ## Wrangling
  signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = all_of(score_name),
              id_cols = c(sampleID,Condition)) %>%
  arrange(Condition)

  ## Matrix Generation
  mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()
  
  ## z-scoring
  scaled_mat <- scale(mat)
  
  ## color function
  starting_point <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[1]
  first_quantile <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[2]
  median_value <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[3]
  third_quantile <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[5]
  # end_point <- summary(signatures_main_annotated_rbind %>% 
  #                             dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
  #                             apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
  #                             data.frame() %>%
  #                             dplyr::pull(all_of(score_name)))[6]

  col_fun <- circlize::colorRamp2(breaks = c(starting_point,
                                             first_quantile,
                                             median_value,
                                             third_quantile
#                                             end_point
                                             ),
                                  colors = viridis(4))


  ## row annotation
  row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = '#0C4B8E',
                                                          "Normoxia" = '#BF382A')
                                            )
                                          )
  
  ## column annotation
  score_wd_df <- signatures_metrics_wd_rbind_df %>% dplyr::filter(score == score_name)
  col_ha <- ComplexHeatmap::HeatmapAnnotation(
    WD = ComplexHeatmap::anno_barplot(x = log1p(score_wd_df$d.wass.2)),
    pvalues = ifelse(score_wd_df$pval < 0.05, "Sig", "Not Sig"),
    col = list(
      pvalues = c("Sig" ="red",
                  "Not Sig" = "purple")
    ))

  h1 <- ComplexHeatmap::Heatmap(matrix = scaled_mat,
                          show_row_names = F,
                          name = score_name,
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off column clustering
                          cluster_columns = F,
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha,
                          # column annotation
                          top_annotation = col_ha,
                          # Color Function (To Control for Outliers)
                          col = col_fun
                          )
  return(h1)
})
names(score_heatmaps) <- scores[-7]

# Saving
dir.create("../Write/Figures/Heatmaps_ZScore_C/HCC1806/", recursive = T)
map(names(score_heatmaps)[-7], function(score_name){
      png(file = paste0("../Write/Figures/Heatmaps_ZScore_C/HCC1806/", score_name,".png"),
          width = 1000,
          height = 1000)
  print(score_heatmaps[[score_name]])
  dev.off()
      })
```

##### WD Calculation (Original + Simulations)

-   The WD calculation here was done on the cluster, so code is commented out.

```{r}
# signatures
## Replacing NA Values
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df <- sig_df %>% replace(is.na(.), 0)
  return(sig_df)
})

## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})


## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)


# scoring functions
scorers <- my_scores

# WD Distance Calculation=======
## WD Metrics
spec.output <- c("pval","d.wass^2","perc.loc","perc.size","perc.shape")


# ## WD Run
# tic()
# signatures_metrics_wd <- map(.x = names(signatures_main), function(sig_name){
#   map(scorers, function(score_name){
#     map(0:1000, function(run_number){
#       # Hypoxic Scores
#       v1 <- signatures_main[[sig_name]] %>% 
#         dplyr::filter(run == run_number) %>%
#         dplyr::filter(Condition == "Hypoxia") %>%
#         pull(score_name)
#       
#       # Normoxic Scores
#       v2 <- signatures_main[[sig_name]] %>%
#         dplyr::filter(run == run_number) %>%
#         dplyr::filter(Condition == "Normoxia") %>%
#         pull(score_name)
#       
#       # WD Function
#       wd <- waddR::wasserstein.test(x = v1, y = v2, method = "ASY")[spec.output]
#       return(wd)
#     }) %>% setNames(as.character(0:1000))
#     }) %>% setNames(scorers)
#   }) %>% setNames(names(signatures_main)) 
# toc()
# 
# ## results saving
# write_rds(x = signatures_metrics_wd,file = "../Intermediate/signature_metrics_wd_1000_HCC1806.rds")

# rbinding results======
## import
signatures_metrics_wd <- readRDS(file = "../SigScores.Cluster/HCC1806/Write/signature_metrics_wd_1000_HCC1806.rds")
# signatures_metrics_wd_modified <- map(names(signatures_metrics_wd), function(sig_name){
#   map(names(signatures_metrics_wd[[sig_name]]), function(score_name){
#     return(signatures_metrics_wd[[sig_name]][[score_name]][0:101])
#     }) %>% setNames(nm = names(signatures_metrics_wd[[1]]))
#   }) %>% setNames(nm = names(signatures_metrics_wd))

## rbind (score level)
signatures_metrics_wd_rbind <- map(names(signatures_metrics_wd), function(sig_name){
  map(scorers, function(score_name){
    aggregated_scorers <- do.call(what = rbind, 
            args = signatures_metrics_wd[[sig_name]][[score_name]]) %>% 
      data.frame() %>%
      dplyr::mutate(run = 0:1000, 
                    score = rep(score_name, times = nrow(.)))
    return(aggregated_scorers)
  }) %>% setNames(scorers)
}) %>% setNames(names(signatures_metrics_wd))

## rbind (signature level)
signatures_metrics_wd_rbind_2 <- map(names(signatures_metrics_wd_rbind),
                                  function(sig_name){
                                    sig_rbind_df <- do.call(rbind, signatures_metrics_wd_rbind[[sig_name]]) %>% 
                                      data.frame() %>% 
                                      mutate(signature = rep(sig_name, times = nrow(.)))
                                    return(sig_rbind_df)
                                  }) %>% setNames(names(signatures_metrics_wd_rbind))

## rbind (final level)
signatures_metrics_wd_rbind_3 <- do.call(rbind, signatures_metrics_wd_rbind_2)
rownames(signatures_metrics_wd_rbind_3) <- NULL

# Significance Calculation========
## Calculation
significance_list <- map(unique(signatures_metrics_wd_rbind_3$signature), function(sig_name){
  map(scorers, function(score_name){
    main_run <- signatures_metrics_wd_rbind_3 %>% 
      dplyr::filter(score == score_name & signature == sig_name & run == 0)
    
    if(is.na(main_run$perc.loc)){
      significance <- NA
    } else{
      # Main Run Distance
      main_run <- signatures_metrics_wd_rbind_3 %>% 
        dplyr::filter(score == score_name & signature == sig_name & run == 0) %>%
        pull(d.wass.2)
    # Sim Runs Distances
    sim_runs <- signatures_metrics_wd_rbind_3 %>% 
      dplyr::filter(score == score_name & signature == sig_name & run != 0) %>%
      pull(d.wass.2)
    # Significance Calculation
    significance <- sum(as.numeric(sim_runs > main_run)) / 1001
    
    # Final Value
    return(significance)
    }
    }) %>% setNames(scorers)
  }) %>% setNames(unique(signatures_metrics_wd_rbind_3$signature))

## score rbind
significance_list_rbind <- map(names(significance_list),function(sig_name){
  signature_significance_df <- do.call(rbind, significance_list[[sig_name]]) %>% 
    data.frame() %>%
    dplyr::rename(.data = ., pval = `.`) %>%
    rownames_to_column("score") %>% 
    dplyr::mutate(signature = rep(sig_name, times = nrow(.)))
  return(signature_significance_df)
  }) %>% setNames(names(significance_list))

## signature rbind
significance_list_rbind_2 <- do.call(rbind, significance_list_rbind)
rownames(significance_list_rbind_2) <- NULL

# Replacing NAs========
significance_list_rbind_2 <- significance_list_rbind_2 %>% 
  mutate(
    pval = ifelse(is.na(pval),999, pval))


# Arranging Signatures by Bulk Order=====
significance_list_rbind_2 <- significance_list_rbind_2 %>% dplyr::mutate(signature = factor(signature, levels = c("Tardon_2020","Ye_2018","Lombardi_2022","Toustrup_2011","Yang_2018_Sarcoma","Khouzam_2021","Mense_2006","Lendhal_2009","Zhang_2021","Sung_2007", "Sorensen_2010","Santamaria_2022","Wang_2005","Benita_2009","Chen_2019","Chi_2006","Aprelikova_2006","Elvidge_2006","Fardin_2009","Beyer_2008","Denko_2003", "Eustace_2013","Lin_2020","Lane_2022","Boidot_2014_Continuous_Hypoxia","Buffa_2010","Detwiller_2005","Jogi_2004","Starmans_2012","Zhao_2021","Halle_2012","Hu_2009","Bosco_2006","Manalo_2005", "Xia_2021","Fardin_2010","Wei_2021","Ghazoui_2011","Li_2021","Winter_2007","Yang_2017","Fjeldbo_2016","Mo_2020","Wang_2020","Yang_2018_Prostate","Koong_2000", "Ning_2004","Shu_2017","Ragnum_2015","Van_malenstein_2010","Peters_2006","Zou_2019","Sun_2021","Seigneuric_2007_early2","Ghorbel_2010","Shi_2007","He_2021","Seigneuric_2007_early0", "Boidot_2014_Cyclic_Hypoxia","Shou_2021","Seigneuric_2007_common","Xu_2022","Gao_2021","Wang_2022", "Shi_2021","Shou_2020","Trong_2018","Sun_2020","Liu_2022","Zhang_2020"))) %>% arrange(signature)


# # Replacing Zeroes=======
# significant_list_replacement_scorers <- map(scorers, function(score_name){
#   
#   # minimum non-zero value computation
#   min_value <- significance_list_rbind_2 %>% 
#     filter(score == score_name & pval != 0) %>% 
#     summarise(min_value = min(pval)) %>% 
#     pull(min_value)
#   
#   # zero replacement (with minimum non-zero value)
#   significance_list_rbind_2_replacement <- significance_list_rbind_2 %>% 
#   filter(score == score_name) %>% 
#   mutate(pval_rep = ifelse(pval == 0, min_value, pval))
#   return(significance_list_rbind_2_replacement)
# }) %>% 
#   # list elements names
#   setNames(scorers) %>% 
#   # rbind step
#   do.call(what = rbind, args = .)
# rownames(significant_list_replacement_scorers) <- NULL

# Flip Check (Hypoxia Lower Than Normoxia)=========
## Check
flip_check <- map(.x = unique(significance_list_rbind_2$signature), 
                              .f = function(sig_name){
                                map(scorers, function(score_name){
                                  # hypoxic score distribution
                                  hypoxic_score_distribution <- signatures_main_annotated_rbind %>% 
                                    filter(run == 0 & Condition == "Hypoxia" & signature == sig_name) %>%
                                    pull(score_name) %>% 
                                    summary()
                                  
                                  # normoxic score distribution
                                  normoxic_score_distribution <- signatures_main_annotated_rbind %>% 
                                    filter(run == 0 & Condition == "Normoxia" & signature == sig_name) %>%
                                    pull(score_name) %>% 
                                    summary()
  flip_check <- hypoxic_score_distribution["Median"] > normoxic_score_distribution["Median"]
  return(flip_check)
                                }) %>% setNames(scorers)
                                }) %>% setNames(unique(significance_list_rbind_2$signature))

## rbind
flip_check_rbind <- map(names(flip_check),function(sig_name){
  flip_check_df <- do.call(rbind, flip_check[[sig_name]]) %>% 
  data.frame() %>% 
  rownames_to_column("score") %>% 
  dplyr::rename("flip_check" = "Median") %>%
  dplyr::mutate(signature = rep(sig_name, nrow(.)))

  return(flip_check_df)
  }) %>% setNames(names(flip_check))

## rbind 2
flip_check_rbind_2 <-  do.call(rbind, flip_check_rbind)
rownames(flip_check_rbind_2) <- NULL


# Adding to Significance List========
significance_list_rbind_2_FlipCheck <- significance_list_rbind_2 %>% left_join(y = flip_check_rbind_2, by = c("signature","score"))
significance_list_rbind_2_FlipCheck <- significance_list_rbind_2_FlipCheck %>% dplyr::mutate(pval= ifelse(flip_check == F, 999, pval))

# Categorical Conversion=====
significance_list_rbind_2_FlipCheck <- significance_list_rbind_2_FlipCheck %>% 
  mutate(pval_cat = ifelse(pval < 0.05, "sig", "non-sig"))

# Replacing NAs=======
significance_list_rbind_2_FlipCheck <- significance_list_rbind_2_FlipCheck %>% 
  dplyr::mutate(pval_cat = ifelse(is.na(pval_cat), "non-sig",pval_cat))
```

##### Heatmap Function (WD Calculation) (Original + Simulations) (Custom Scale)

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Score Heatmaps
scores <- sigscores::getAvailableScores() %>% 
#  dplyr::filter(!id %in% c("mode","iqm")) %>% 
  pull(id)

score_heatmaps <- map(scores[-7], function(score_name){

  ## Wrangling
  signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = all_of(score_name),
              id_cols = c(sampleID,Condition)) %>%
    arrange(Condition) %>%
    dplyr::select(Tardon_2020,Ye_2018,Lombardi_2022,Toustrup_2011,Yang_2018_Sarcoma,Khouzam_2021,Mense_2006,Lendhal_2009,Zhang_2021,Sung_2007, Sorensen_2010,Santamaria_2022,Wang_2005,Benita_2009,Chen_2019,Chi_2006,Aprelikova_2006,Elvidge_2006,Fardin_2009,Beyer_2008,Denko_2003, Eustace_2013,Lin_2020,Lane_2022,Boidot_2014_Continuous_Hypoxia,Buffa_2010,Detwiller_2005,Jogi_2004,Starmans_2012,Zhao_2021,Halle_2012,Hu_2009,Bosco_2006,Manalo_2005, Xia_2021,Fardin_2010,Wei_2021,Ghazoui_2011,Li_2021,Winter_2007,Yang_2017,Fjeldbo_2016,Mo_2020,Wang_2020,Yang_2018_Prostate,Koong_2000, Ning_2004,Shu_2017,Ragnum_2015,Van_malenstein_2010,Peters_2006,Zou_2019,Sun_2021,Seigneuric_2007_early2,Ghorbel_2010,Shi_2007,He_2021,Seigneuric_2007_early0, Boidot_2014_Cyclic_Hypoxia,Shou_2021,Seigneuric_2007_common,Xu_2022,Gao_2021,Wang_2022, Shi_2021,Shou_2020,Trong_2018,Sun_2020,Liu_2022,Zhang_2020, everything())

  ## Matrix Generation
  mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()
  
  ## z-scoring
  scaled_mat <- scale(mat)
  
  ## color function
  starting_point <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[1]
  first_quantile <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[2]
  median_value <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[3]
  third_quantile <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[5]
  # end_point <- summary(signatures_main_annotated_rbind %>% 
  #                             dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
  #                             apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
  #                             data.frame() %>%
  #                             dplyr::pull(all_of(score_name)))[6]

  col_fun <- circlize::colorRamp2(breaks = c(starting_point,
                                             first_quantile,
                                             median_value,
                                             third_quantile
#                                             end_point
                                             ),
                                  colors = viridis(4))


  ## row annotation
  row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = '#0C4B8E',
                                                          "Normoxia" = '#BF382A')
                                            )
                                          )
  
  ## column annotation
  score_pval_df <- significance_list_rbind_2_FlipCheck %>% dplyr::filter(score == score_name)
  col_ha <- ComplexHeatmap::HeatmapAnnotation(
    pval = score_pval_df$pval_cat,
    col = list(pval = c("sig" = "red", "non-sig" = "blue"))
    )
  
  ## column names (symbol added for data source)
  sig_names_source <- c('Tardon *','Ye *','Lombardi *','Toustrup *','Yang 2018 Sarcoma * °','Khouzam *','Mense *','Lendhal *','Zhang 2021 *','Sung *','Sorensen *','Santamaria * °','Wang 2005 *','Benita *','Chen *','Chi *','Aprelikova *','Elvidge *','Fardin 2009 *','Beyer *','Denko *','Eustace °','Lin °','Lane *','Boidot Cont. * °','Buffa * °','Detwiller *','Jogi *','Starmans *','Zhao °','Halle * °','Hu °','Bosco *','Manalo *','Xia °','Fardin 2010 *','Wei °','Ghazoui °','Li °','Winter °','Yang 2017 °','Fjeldbo °','Mo °','Wang 2020 °','Yang 2018 Prostate * °','Koong *','Ning *','Suh *','Ragnum * °','Van Malenstein *','Peters *','Zou °','Sun 2021 * °','Seigneuric E2 *','Ghorbel °','Shi *','He °','Seigneuric E0 *','Boidot Cyc. * °','Shou 2021 °','Seigneuric C. *','Xu * °','Gao °','Wang 2022 °','Shi 2021 °','Shou 2020 °','Trong *','Sun 2020 °','Liu °','Zhang 2020 * °')
  
  ## heatmap
  h1 <- ComplexHeatmap::Heatmap(matrix = scaled_mat,
                          show_row_names = F,
                          name = score_name,
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off column clustering
                          cluster_columns = F,
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha,
                          # column annotation
                          top_annotation = col_ha,
                          # Color Function (To Control for Outliers)
                          col = col_fun,
                          # Column Names (Custom)
                          column_labels = sig_names_source
                          )
  return(h1)
})
names(score_heatmaps) <- scores[-7]

# Saving
dir.create("../Write/Figures/Heatmaps_ZScore_PVAL/HCC1806/", recursive = T)
map(names(score_heatmaps)[-7], function(score_name){
      png(file = paste0("../Write/Figures/Heatmaps_ZScore_PVAL/HCC1806/", score_name,".png"),
          width = 1000,
          height = 1000)
  print(score_heatmaps[[score_name]])
  dev.off()
      })
```

##### Heatmap Function (WD Calculation) (Original + Simulations) (Automatic Scale)

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Score Heatmaps
scores <- sigscores::getAvailableScores() %>% 
#  dplyr::filter(!id %in% c("mode","iqm")) %>% 
  pull(id)

score_heatmaps <- map(scores, function(score_name){

  ## Wrangling
  signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = all_of(score_name),
              id_cols = c(sampleID,Condition)) %>%
    arrange(Condition) %>%
    dplyr::select(Tardon_2020,Ye_2018,Lombardi_2022,Toustrup_2011,Yang_2018_Sarcoma,Khouzam_2021,Mense_2006,Lendhal_2009,Zhang_2021,Sung_2007, Sorensen_2010,Santamaria_2022,Wang_2005,Benita_2009,Chen_2019,Chi_2006,Aprelikova_2006,Elvidge_2006,Fardin_2009,Beyer_2008,Denko_2003, Eustace_2013,Lin_2020,Lane_2022,Boidot_2014_Continuous_Hypoxia,Buffa_2010,Detwiller_2005,Jogi_2004,Starmans_2012,Zhao_2021,Halle_2012,Hu_2009,Bosco_2006,Manalo_2005, Xia_2021,Fardin_2010,Wei_2021,Ghazoui_2011,Li_2021,Winter_2007,Yang_2017,Fjeldbo_2016,Mo_2020,Wang_2020,Yang_2018_Prostate,Koong_2000, Ning_2004,Shu_2017,Ragnum_2015,Van_malenstein_2010,Peters_2006,Zou_2019,Sun_2021,Seigneuric_2007_early2,Ghorbel_2010,Shi_2007,He_2021,Seigneuric_2007_early0, Boidot_2014_Cyclic_Hypoxia,Shou_2021,Seigneuric_2007_common,Xu_2022,Gao_2021,Wang_2022, Shi_2021,Shou_2020,Trong_2018,Sun_2020,Liu_2022,Zhang_2020, everything())

  ## Matrix Generation
  mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()
  
  ## z-scoring
  scaled_mat <- scale(mat)
  
#   ## color function
#   starting_point <- summary(signatures_main_annotated_rbind %>% 
#                               dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
#                               apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
#                               data.frame() %>%
#                               dplyr::pull(all_of(score_name)))[1]
#   first_quantile <- summary(signatures_main_annotated_rbind %>% 
#                               dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
#                               apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
#                               data.frame() %>%
#                               dplyr::pull(all_of(score_name)))[2]
#   median_value <- summary(signatures_main_annotated_rbind %>% 
#                               dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
#                               apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
#                               data.frame() %>%
#                               dplyr::pull(all_of(score_name)))[3]
#   third_quantile <- summary(signatures_main_annotated_rbind %>% 
#                               dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
#                               apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
#                               data.frame() %>%
#                               dplyr::pull(all_of(score_name)))[5]
#   # end_point <- summary(signatures_main_annotated_rbind %>% 
#   #                             dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
#   #                             apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
#   #                             data.frame() %>%
#   #                             dplyr::pull(all_of(score_name)))[6]
# 
#   col_fun <- circlize::colorRamp2(breaks = c(starting_point,
#                                              first_quantile,
#                                              median_value,
#                                              third_quantile
# #                                             end_point
#                                              ),
#                                   colors = viridis(4))


  ## row annotation
  row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = '#0C4B8E',
                                                          "Normoxia" = '#BF382A')
                                            )
                                          )
  
  ## column annotation
  score_pval_df <- significance_list_rbind_2_FlipCheck %>% dplyr::filter(score == score_name)
  col_ha <- ComplexHeatmap::HeatmapAnnotation(
    pval = score_pval_df$pval_cat,
    col = list(pval = c("sig" = "red", "non-sig" = "blue"))
    )
  
  ## column names (symbol added for data source)
  sig_names_source <- c('Tardon *','Ye *','Lombardi *','Toustrup *','Yang 2018 Sarcoma * °','Khouzam *','Mense *','Lendhal *','Zhang 2021 *','Sung *','Sorensen *','Santamaria * °','Wang 2005 *','Benita *','Chen *','Chi *','Aprelikova *','Elvidge *','Fardin 2009 *','Beyer *','Denko *','Eustace °','Lin °','Lane *','Boidot Cont. * °','Buffa * °','Detwiller *','Jogi *','Starmans *','Zhao °','Halle * °','Hu °','Bosco *','Manalo *','Xia °','Fardin 2010 *','Wei °','Ghazoui °','Li °','Winter °','Yang 2017 °','Fjeldbo °','Mo °','Wang 2020 °','Yang 2018 Prostate * °','Koong *','Ning *','Suh *','Ragnum * °','Van Malenstein *','Peters *','Zou °','Sun 2021 * °','Seigneuric E2 *','Ghorbel °','Shi *','He °','Seigneuric E0 *','Boidot Cyc. * °','Shou 2021 °','Seigneuric C. *','Xu * °','Gao °','Wang 2022 °','Shi 2021 °','Shou 2020 °','Trong *','Sun 2020 °','Liu °','Zhang 2020 * °')
  
  ## heatmap
  h1 <- ComplexHeatmap::Heatmap(matrix = scaled_mat,
                          show_row_names = F,
                          name = score_name,
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off column clustering
                          cluster_columns = F,
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha,
                          # column annotation
                          top_annotation = col_ha,
                          # Color Function (To Control for Outliers)
                        #  col = col_fun,
                          # Column Names (Custom)
                          column_labels = sig_names_source
                          )
  return(h1)
})
names(score_heatmaps) <- scores

# Saving
dir.create("../Write/Figures/Heatmaps_ZScore_PVAL_NO_CUSTOM_SCALE/HCC1806/", recursive = T)
map(names(score_heatmaps), function(score_name){
      png(file = paste0("../Write/Figures/Heatmaps_ZScore_PVAL_NO_CUSTOM_SCALE/HCC1806/", score_name,".png"),
          width = 1000,
          height = 1000)
  print(score_heatmaps[[score_name]])
  dev.off()
      })
```

##### Heatmap Function (WD Calculation) (Original + Simulations) (Automatic Scale) (Custom Colors)

```{r}
# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)


## Scorers
scores <- my_scores

## Colors
hex_list <- list(
  c("#440154FF", "white", "#21908CFF"),
  c("#440154FF", "white", "#FDE725FF"),
  c("black", "white", "#FEE715"),
  c("#ff1493", "white", "#003546")
)



# Score Heatmaps Function
generate_heatmaps <- function(scores, colors){
  score_heatmaps <- map(scores, function(score_name){
    ## Wrangling
    signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
      pivot_wider(names_from = signature,
                  values_from = all_of(score_name),
                  id_cols = c(sampleID,Condition)) %>%
      arrange(Condition) %>%
      dplyr::select(Tardon_2020,Ye_2018,Lombardi_2022,Toustrup_2011,Yang_2018_Sarcoma,Khouzam_2021,Mense_2006,Lendhal_2009,Zhang_2021,Sung_2007, Sorensen_2010,Santamaria_2022,Wang_2005,Benita_2009,Chen_2019,Chi_2006,Aprelikova_2006,Elvidge_2006,Fardin_2009,Beyer_2008,Denko_2003, Eustace_2013,Lin_2020,Lane_2022,Boidot_2014_Continuous_Hypoxia,Buffa_2010,Detwiller_2005,Jogi_2004,Starmans_2012,Zhao_2021,Halle_2012,Hu_2009,Bosco_2006,Manalo_2005, Xia_2021,Fardin_2010,Wei_2021,Ghazoui_2011,Li_2021,Winter_2007,Yang_2017,Fjeldbo_2016,Mo_2020,Wang_2020,Yang_2018_Prostate,Koong_2000, Ning_2004,Shu_2017,Ragnum_2015,Van_malenstein_2010,Peters_2006,Zou_2019,Sun_2021,Seigneuric_2007_early2,Ghorbel_2010,Shi_2007,He_2021,Seigneuric_2007_early0, Boidot_2014_Cyclic_Hypoxia,Shou_2021,Seigneuric_2007_common,Xu_2022,Gao_2021,Wang_2022, Shi_2021,Shou_2020,Trong_2018,Sun_2020,Liu_2022,Zhang_2020, everything())
    
    ## Matrix Generation
    mat <- signatures_main_annotated_rbind_pivot %>%
      dplyr::select(-Condition) %>%
      column_to_rownames("sampleID") %>%
      as.matrix()
    
    ## z-scoring
    scaled_mat <- scale(mat)
    
    col_fun <- circlize::colorRamp2(breaks = c(-2, 0, 2),
                                    colors = colors)


    ## row annotation
    row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                            col = list(
                                              Condition = c("Hypoxia" = '#0C4B8E',
                                                            "Normoxia" = '#BF382A')
                                              )
                                            )
  
    ## column annotation
    score_pval_df <- significance_list_rbind_2_FlipCheck %>% dplyr::filter(score == score_name)
    col_ha <- ComplexHeatmap::HeatmapAnnotation(
      pval = score_pval_df$pval_cat,
      col = list(pval = c("sig" = "red", "non-sig" = "blue"))
      )
  
    ## column names (symbol added for data source)
    sig_names_source <- c('Tardon *','Ye *','Lombardi *','Toustrup *','Yang 2018 Sarcoma * °','Khouzam *','Mense *','Lendhal *','Zhang 2021 *','Sung *','Sorensen *','Santamaria * °','Wang 2005 *','Benita *','Chen *','Chi *','Aprelikova *','Elvidge *','Fardin 2009 *','Beyer *','Denko *','Eustace °','Lin °','Lane *','Boidot Cont. * °','Buffa * °','Detwiller *','Jogi *','Starmans *','Zhao °','Halle * °','Hu °','Bosco *','Manalo *','Xia °','Fardin 2010 *','Wei °','Ghazoui °','Li °','Winter °','Yang 2017 °','Fjeldbo °','Mo °','Wang 2020 °','Yang 2018 Prostate * °','Koong *','Ning *','Suh *','Ragnum * °','Van Malenstein *','Peters *','Zou °','Sun 2021 * °','Seigneuric E2 *','Ghorbel °','Shi *','He °','Seigneuric E0 *','Boidot Cyc. * °','Shou 2021 °','Seigneuric C. *','Xu * °','Gao °','Wang 2022 °','Shi 2021 °','Shou 2020 °','Trong *','Sun 2020 °','Liu °','Zhang 2020 * °')
  
    ## heatmap
    h1 <- ComplexHeatmap::Heatmap(matrix = scaled_mat,
                            show_row_names = F,
                            name = score_name,
                            # Column Title
                            column_title = "Signatures",
                            # Row Title
                            row_title = "Cells",
                            column_title_side = "bottom",
                            # Turning off column clustering
                            cluster_columns = F,
                            # Turning off row clustering
                            cluster_rows = F,
                            # row annotation
                            right_annotation = row_ha,
                            # column annotation
                            top_annotation = col_ha,
                            # Color Function (To Control for Outliers)
                            col = col_fun,
                            # Column Names (Custom)
                            column_labels = sig_names_source
                            )
    return(h1)
  })
  names(score_heatmaps) <- scores
  # Create a directory name based on colors
  dir_name <- paste0("../Write/Figures/Heatmaps_Final/HCC1806/", 
                     colors[1],
                     "_to_",
                     colors[2],
                     "_to_",
                     colors[3],"/")
  dir.create(dir_name, recursive = T)
  map2(names(score_heatmaps), 33:50, function(score_name, number) {
    png(file = paste0(dir_name, "Figure_S", number, score_name, ".png"),
        width = 1000,
        height = 1000)
    print(score_heatmaps[[score_name]])
    dev.off()
  })
  # returning the heatmaps themselves
  return(score_heatmaps)
}

# Function Call
score_heatmaps_colors <- map(hex_list, function(x){
  generate_heatmaps(my_scores, colors = x)
})

# Saving for Shiny App
saveRDS(
  object = score_heatmaps_colors[[2]],
  file = "../Intermediate/score_heatmaps_HCC1806.rds"
)
```

##### Fardin Manual ComplexHeatmap

```{r}
# Signature Features Import
signature_features <- readRDS("../Read/SigRListAnnotated.rds")
fardin_features <- signature_features$Fardin_2010$hgnc_symbol
cell_order <- HCC1806NISub@meta.data %>% dplyr::arrange(desc(Condition)) %>% rownames()

# count matrix 
fardin_count_matrix <- t(as.matrix(HCC1806NISub@assays$SCT@data[fardin_features,cell_order]))


# row annotation
row_ha <- ComplexHeatmap::rowAnnotation(Condition =  HCC1806NISub@meta.data %>% dplyr::arrange(desc(Condition)) %>% pull(Condition),
                                          col = list(
                                            Condition = c("Hypoxia" = '#0C4B8E',
                                                          "Normoxia" = '#BF382A')
                                            )
                                          )

# heatmap function
h1 <- ComplexHeatmap::Heatmap(matrix = fardin_count_matrix,
                              show_row_names = F,
                              name = "Fardin_Features",
                              # Column Title
                              column_title = "Features",
                              # Row Title
                              row_title = "Cells",
                              column_title_side = "bottom",
                              # Turning off column clustering
                              cluster_columns = T,
                              # Turning off row clustering
                              cluster_rows = F,
                              # row annotation
                              right_annotation = row_ha
                              )
png(file = paste0("../Write/Figures/", "HCC1806_Fardin_2010_Troubleshoot",".png"),
          width = 1000,
          height = 1000)
print(h1)
dev.off()
```

##### Scaled Matrix Boxplot

```{r}
# Available Scores
scores <- my_scores

# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

# delete later (quick fix)
signatures_main <- signatures_main[-1] 

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Boxplot
## singular Implementation
  signatures_main_annotated_rbind %>% 
    group_by(signature) %>% 
    mutate(z_iqm = scale(iqm)) %>% 
    ggplot(aes(x = signature, y = z_iqm)) + 
    geom_boxplot(aes(fill = signature)) + 
    facet_grid(. ~ Condition) + 
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
ggsave(filename = "myfigure.jpg",height = 10, width = 20)

## scaled Implementation
map(scores, function(colname) {
  p1 <- signatures_main_annotated_rbind %>% 
    group_by(signature) %>% 
    mutate(z_score = scale(.data[[colname]])) %>% 
    ggplot(aes(x = signature, y = z_score)) + 
    geom_boxplot(aes(fill = signature)) + 
    facet_grid(. ~ Condition) + 
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    labs(title = paste("Boxplot of Z-scored", colname),
         y = "Z-score")
  ggsave(plot = p1, 
         filename = paste0("../Write/Figures/Boxplots/HCC1806/", colname,".jpg"),
         height = 10, 
         width = 20)
  })
```




````{=html}
<!--

#### Manual Color Scale

-   I got the same warning from the heatmap code above that there are outliers even after z-scoring, so I created the code below to apply the manual color scale even after z-scoring and I compared the results.

    -   Sadly, I still had to remove `mode` and `iqm` from the heatmap code below because there were no distinct breaks for the different quantiles when setting the manual scale.

-   I compared the heatmaps generated before and after the manual scale for z-scoring, and the results seem comparable so I am going against manual scales and sticking with the automatic one.

```{r}


# Data Wrangling
## Filtering For The Main Run
signatures_main <- map(.x = signatures, .f = function(sig_df){
  sig_df_run0 <- sig_df %>% filter(run == 0)
  return(sig_df_run0)
})

## Adding Sig names to signature list & Rbinding
signatures_main_annotated <- map(names(signatures_main),
    function(sig_name){
      signature_of_interest <- signatures_main[[sig_name]]
      signature_of_interest$signature <- rep(x = sig_name,nrow(signature_of_interest))
      return(signature_of_interest)
    })
names(signatures_main_annotated) <- names(signatures_main)
signatures_main_annotated_rbind <- do.call(what = rbind, args = signatures_main_annotated)

# Score Heatmaps
scores <- sigscores::getAvailableScores() %>% 
  dplyr::filter(!id %in% c("mode","iqm")) %>% 
  pull(id)

score_heatmaps <- map(scores, function(score_name){

  ## Wrangling
  signatures_main_annotated_rbind_pivot <- signatures_main_annotated_rbind %>%
  pivot_wider(names_from = signature,
              values_from = all_of(score_name),
              id_cols = c(sampleID,Condition)) %>%
  arrange(Condition)

  ## Matrix Generation
  mat <- signatures_main_annotated_rbind_pivot %>%
    dplyr::select(-Condition) %>%
    column_to_rownames("sampleID") %>%
    as.matrix()
  scaled_mat <- scale(mat)
  ## color function
  starting_point <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[1]
  first_quantile <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[2]
  median_value <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[3]
  third_quantile <- summary(signatures_main_annotated_rbind %>% 
                              dplyr::select(-c(sampleID, run, signature, Condition)) %>% 
                              apply(MARGIN = 2, FUN = function(x){scale(x)}) %>% 
                              data.frame() %>%
                              dplyr::pull(all_of(score_name)))[5]

  col_fun <- circlize::colorRamp2(breaks = c(starting_point,
                                             first_quantile,
                                             median_value,
                                             third_quantile),
                                  colors = c("blue",
                                                   "green",
                                                   "yellow",
                                                   "red"))


  ## row annotation
  row_ha <- ComplexHeatmap::rowAnnotation(Condition = signatures_main_annotated_rbind_pivot$Condition,
                                          col = list(
                                            Condition = c("Hypoxia" = "blue",
                                                          "Normoxia" = "red"))
                                          )


  h1 <- ComplexHeatmap::Heatmap(matrix = scaled_mat,
                          show_row_names = F,
                          name = score_name,
                          # Column Title
                          column_title = "Signatures",
                          # Row Title
                          row_title = "Cells",
                          column_title_side = "bottom",
                          # Turning off column clustering
                          cluster_columns = F,
                          # Turning off row clustering
                          cluster_rows = F,
                          # row annotation
                          right_annotation = row_ha,
                          # Color Function (To Control for Outliers)
                          col = col_fun
                          )
  return(h1)
})
names(score_heatmaps) <- scores
# Saving
dir.create("../Write/Figures/Heatmaps_ZScore_ManualScale/HCC1806/", recursive = T)
map(names(score_heatmaps), function(score_name){
      png(file = paste0("../Write/Figures/Heatmaps_ZScore_ManualScale/HCC1806/", score_name,".png"),
          width = 1000,
          height = 1000)
  print(score_heatmaps[[score_name]])
  dev.off()
      })
```

-->
````

## Density Plot

-   Code below is straight forward but highly effective. I add an annotation to distinguish the original run from the simulations.

-   I then use a double map call to iterate through every single df and every single score to create the necessary density plots.

-   These are two density plots that are split by runtype (original or simulation) and colored/filled by condition.

    -   The purpose of this plot is to show that simulations with random signatures have no difference in their distribution whereas the original signature shows a clear separation of the distribution between the normoxic and hypoxic samples.

```{r}
# Adding Annotation for Original vs Simulation
signatures_annotated <- map(.x = signatures,
    .f = function(sig_df){
      sig_df %>% mutate(runtype = ifelse(run == 0, "original", "simulation"))
    })

# available scores
available_scores <- sigscores::getAvailableScores()$id

# Double Map Call for Density Plot Creation
density_plots <- map(signatures_annotated,
                     .f = function(sig_df){
  map(available_scores, function(score_name){
    p <- sig_df %>%
      ggplot(aes(x = .data[[score_name]])) +
               geom_density(aes(color = Condition, fill = Condition)) +
               facet_grid(runtype ~ ., scales = "free_y") + labs(x = score_name,
                                                                 title = score_name)
    return(p)
  }) %>% setNames(available_scores)
  }) %>% setNames(names(signatures_annotated))

# Map Call for Directory Creation Per Signature
map(names(density_plots), function(sig_name){
  dir.create(path = paste0("../Write/Figures/Density/HCC1806/",sig_name))})

# Double Map Call for Saving Each Score Figure Per Signature
map(names(density_plots), function(sig_name){
  map(available_scores, function(score_name){
    ggsave(plot = density_plots[[sig_name]][[score_name]],
           filename = paste0("../Write/Figures/Density/HCC1806/",
                             sig_name, "/",
                             score_name,".png"),
           height = 15,
           width = 15)
  })
})
```

## Rain Cloud Plots

```{r}
# Adding Annotation for Original vs Simulation
signatures_annotated <- map(.x = signatures,
    .f = function(sig_df){
      sig_df %>% mutate(runtype = ifelse(run == 0, "original", "simulation"))
    })

# available scores
available_scores <- my_scores
# Double Map Call for Raincloud Plot Creation (Original)
raincloud_plots_original <- map(signatures_annotated, 
                     .f = function(sig_df){
  map(available_scores, function(score_name){
    p <-  sig_df %>%
      dplyr::filter(runtype == "original") %>%
      ggplot(aes(x = factor(Condition), y = .data[[score_name]], fill = factor(Condition))) +
      # add half-violin from {ggdist} package
      stat_halfeye(
        # adjust bandwidth
        adjust = 0.5,
        # move to the right
        justification = -0.2,
        # remove the slab interval
        .width = 0,
        point_colour = NA) +
        # boxplot
      geom_boxplot(
        width = 0.12,
        # purple outlier points
        outlier.color = "purple",
        alpha = 0.5) +
      # Themes and Labels
      scale_fill_manual(values = c('#0C4B8E', '#BF382A')) +
#      theme_fivethirtyeight() +
      labs(
    title = paste0("raincloud plot of ", score_name," (original)"),
    fill = "Condition"
  ) +
      # Horizontal to vertical  
      coord_flip() +
      theme(
        plot.background = element_rect(fill = "white", colour = "white"),
        panel.background = element_rect(fill = "white", colour = "white")
        )
    return(p)
  }) %>% setNames(available_scores)
  }) %>% setNames(names(signatures_annotated))

# Map Call for Directory Creation Per Signature
map(names(raincloud_plots_original), function(sig_name){
  dir.create(path = paste0("../Write/Figures/RainCloud/HCC1806/Original/",sig_name),
             recursive = T)})

# Double Map Call for Saving Each Score Figure Per Signature
map(names(raincloud_plots_original), function(sig_name){
  map(available_scores, function(score_name){
    ggsave(plot = raincloud_plots_original[[sig_name]][[score_name]],
           filename = paste0("../Write/Figures/RainCloud/HCC1806/Original/",
                             sig_name, "/",
                             score_name,".png"),
           height = 15,
           width = 15)
  })
})



# Double Map Call for Raincloud Plot Creation (Simulation)
raincloud_plots_simulation <- map(signatures_annotated, 
                     .f = function(sig_df){
  map(available_scores, function(score_name){
    p <-  sig_df %>%
      dplyr::filter(runtype == "simulation" & run %in% 1:10) %>%
      ggplot(aes(x = factor(Condition), y = .data[[score_name]], fill = factor(Condition))) +
      # add half-violin from {ggdist} package
      stat_halfeye(
        # adjust bandwidth
        adjust = 0.5,
        # move to the right
        justification = -0.2,
        # remove the slab interval
        .width = 0,
        point_colour = NA) +
        # boxplot
      geom_boxplot(
        width = 0.12,
        # purple outlier points
        outlier.color = "purple",
        alpha = 0.5) +
      # Themes and Labels
      scale_fill_manual(values = c('#0C4B8E', '#BF382A')) +
      theme_fivethirtyeight() +
      labs(
    title = paste0("raincloud plot of ",  score_name," (simulation)"),
    fill = "Condition"
  ) +
  # Horizontal to vertical  
  coord_flip()
    return(p)
  }) %>% setNames(available_scores)
  }) %>% setNames(names(signatures_annotated))


# Map Call for Directory Creation Per Signature
map(names(raincloud_plots_simulation), function(sig_name){
  dir.create(path = paste0("../Write/Figures/RainCloud/HCC1806/Simulation/",sig_name),
             recursive = T)})

# Double Map Call for Saving Each Score Figure Per Signature
map(names(raincloud_plots_simulation), function(sig_name){
  map(available_scores, function(score_name){
    ggsave(plot = raincloud_plots_simulation[[sig_name]][[score_name]],
           filename = paste0("../Write/Figures/RainCloud/HCC1806/Simulation/",
                             sig_name, "/",
                             score_name,".png"),
           height = 15,
           width = 15)
  })
})

# Double Map Call for Raincloud Plot Creation (Original + Simulation)
raincloud_plots_original_simulation <- map(signatures_annotated, 
                     .f = function(sig_df){
  map(available_scores, function(score_name){
    p <-  sig_df %>%
      dplyr::mutate(condition_runtype = paste(Condition, runtype,sep = "_")) %>%
      dplyr::filter(run %in% 0:10) %>%
      ggplot(aes(x = factor(condition_runtype), 
                 y = .data[[score_name]], 
                 fill = factor(condition_runtype))) +
      # add half-violin from {ggdist} package
      stat_halfeye(
        # adjust bandwidth
        adjust = 0.5,
        # move to the right
        justification = -0.2,
        # remove the slab interval
        .width = 0,
        point_colour = NA) +
        # boxplot
      geom_boxplot(
        width = 0.12,
        # purple outlier points
        outlier.color = "purple",
        alpha = 0.5) +
      # Themes and Labels
 #     scale_fill_manual(values = c('#0C4B8E', '#BF382A')) +
#      theme_fivethirtyeight() +
      labs(
    title = paste0("raincloud plot of ",  score_name," (original + simulation)"),
    fill = "Condition & Runtype", 
    x = "Condition & Runtype"
  ) +
  # Horizontal to vertical  
  coord_flip() +
      theme(
        plot.background = element_rect(fill = "white", colour = "white"),
        panel.background = element_rect(fill = "white", colour = "white")
        )
    return(p)
  }) %>% setNames(available_scores)
  }) %>% setNames(names(signatures_annotated))


# Map Call for Directory Creation Per Signature
map(names(raincloud_plots_original_simulation), function(sig_name){
  dir.create(path = paste0("../Write/Figures/RainCloud/HCC1806/OriginalSimulation/",sig_name),
             recursive = T)})

# Double Map Call for Saving Each Score Figure Per Signature
map(names(raincloud_plots_original_simulation), function(sig_name){
  map(available_scores, function(score_name){
    ggsave(plot = raincloud_plots_original_simulation[[sig_name]][[score_name]],
           filename = paste0("../Write/Figures/RainCloud/HCC1806/OriginalSimulation/",
                             sig_name, "/",
                             score_name,".png"),
           height = 15,
           width = 15)
  })
})

```

## Master WD Results Table

```{r}
signatures_metrics_wd_rbind_df %>% 
  dplyr::select(score, d.wass.2, signature) %>% 
  pivot_wider(values_from = d.wass.2, names_from = score) %>% 
  mutate_if(is.numeric, scale) %>%
  data.table::fwrite(file = "../Write/Tables/WD Values_All Scores_HCC1806.csv")
```
